---
title: AO3
author: ''
date: '2022-04-02'
slug: ao3
categories: []
tags: []
---
## Looking at the data sets 
# train
```{r}
titanic_train <-read_csv("https://raw.githubusercontent.com/csanford2020/website_delete/main/train.csv")
str(titanic_train)
summary(titanic_train)
head(titanic_train)
tail(titanic_train)
```
```{r}
titanic_test <- read_csv( "https://raw.githubusercontent.com/csanford2020/website_delete/main/test.csv")
str(titanic_test)
````
```{r}
library(tidyverse)
```
# join the data sets 
```{r}
titanic_train$is_train_set <- TRUE
titanic_test$is_train_set <- FALSE

tail(titanic_test)
tail(titanic_train)
````
# checking equalitly in the data sets 
```{r}
ncol(titanic_test)
ncol(titanic_train)
names(titanic_train)
names(titanic_test)
```
# Add survived colum to the test data set
```{r}
titanic_test$Survived <- NA
sum(is.na(titanic_test$Survived))
```
#Binding the datasets
```{r}
titanic_full <- rbind(titanic_train, titanic_test)
```
## checking the bind dataset
```{r}
colSums(is.na(titanic_full))
sum(is.na(subset(titanic_full, is_train_set==FALSE, select="Survived")))
```
## Checking fare imputations 
```{r}
sum(is.na(titanic_full$Fare))
bp_Fare <- boxplot(titanic_full$Fare)
```
# finding the cutoff point of the outlier in fare
```{r}
boxplot(titanic_full$Fare)
boxplot.stats(titanic_full$Fare)
fare_upper_wishker <- boxplot.stats(titanic_full$Fare)$stats
```
# filter 
```{r}
fare_outlier_filter <- titanic_full$Fare < fare_upper_wishker
titanic_filtered_with_fare <- titanic_full[fare_outlier_filter,]
```
# check filter
```{r}
colSums(is.na(titanic_filtered_with_fare))
titanic_filtered_with_fare_and_without_NA <- titanic_filtered_with_fare %>%
  select(-Cabin, -Survived, -PassengerId, -Name) %>%
  drop_na()
sum(is.na(titanic_filtered_with_fare_and_without_NA))
```
# equation for fare
```{r}
fare_equation = "Fare ~ Pclass + Sex + Age + SibSp + Parch + Embarked"
```
# regression for fare
```{r}
fare_model <- lm(formula = fare_equation, 
                 data = titanic_filtered_with_fare_and_without_NA)
```
```{r}
data_with_missing_fare <- titanic_full[is.na(titanic_full$Fare), 
                           c("Pclass", "Sex", "Age", "SibSp", "Parch", "Embarked")]
```
```{r}
fare_prediction <- predict(fare_model, newdata = data_with_missing_fare)
print(fare_model)
print(data_with_missing_fare)
print(fare_prediction)
```
```{r}
lm(formula = fare_equation, data = titanic_filtered_with_fare_and_without_NA)
```
#  Impute the missing fare with the prediction
```{r}
titanic_full[is.na(titanic_full$Fare), "Fare"] <- fare_prediction
sum(is.na(titanic_full$Fare))
```
## Embarked Imputation
# Prepare
```{r}
titanic_full_cat_casted <- titanic_full %>%
  mutate(
    Pclass = as.integer(as.factor(titanic_full$Pclass)),
    Sex = as.integer(as.factor(titanic_full$Sex)),
    SibSp = as.integer(as.factor(titanic_full$SibSp)),
    Parch = as.integer(as.factor(titanic_full$Parch))
  )

table(titanic_full_cat_casted$Embarked, useNA="always") 
library(class)
embarked_label <- na.omit(titanic_full_cat_casted$Embarked)
unique(embarked_label)
length(embarked_label)
dim(titanic_full_cat_casted)
```
```{r}
# need to drop some rows that has NA in Embarked so the number of rows is equal
titanic_same_length_with_embarked_label <- subset(x = titanic_full_cat_casted,
                                                  subset = !is.na (titanic_full_cat_casted$Embarked))
dim(titanic_same_length_with_embarked_label)


embarked_knn_train <- titanic_same_length_with_embarked_label %>% 
                      select(-Cabin, -Age, -Ticket, -Survived, -Name, -Embarked, -is_train_set) 

colSums(is.na(embarked_knn_train))                             
dim(embarked_knn_train)
length(embarked_label)
sum(is.na(embarked_label))

# row that has NA in embark for the test
titanic_embark <- titanic_full_cat_casted[is.na(titanic_full_cat_casted$Embarked),] 
embarked_test <- titanic_embark %>% 
  select(-Cabin, -Age, -Ticket, -Survived, -Name, -Embarked, -is_train_set) %>%
  drop_na()

# should be 2 rows
dim(embarked_test)
sum(is.na(embarked_test))
```
# finding the missing values in Embarked 
```{r}
embarked_result <- knn(train = embarked_knn_train,
                       test = embarked_test,
                       cl = embarked_label,
                       k=7)
print(embarked_result)
```
```{r}
titanic_full[is.na(titanic_full$Embarked), "Embarked"] <- embarked_result
titanic_full_cat_casted[is.na(titanic_full_cat_casted$Embarked), "Embarked"] <- embarked_result
colSums(is.na(titanic_full)) 
colSums(is.na(titanic_full_cat_casted))
```
```{r}
titanic_full_cat_casted <- titanic_full_cat_casted %>%
  mutate(Embarked = as.integer(as.factor(Embarked)))
```
## Cabin Imputation
# prepare
```{r}
titanic_cabin_label <- str_sub(string = titanic_full_cat_casted$Cabin,  
                               start = 1, 
                               end = 1) %>% na.omit()
length(titanic_cabin_label)
titanic_cabin_train <- titanic_full_cat_casted %>%
  filter(titanic_full_cat_casted$Cabin != is.na(titanic_full_cat_casted$Cabin)) %>%
  select(PassengerId, Pclass, Sex, SibSp, Parch, Fare, Embarked)
dim(titanic_cabin_train)
```
# preparing for the test data frame
```{r}
titanic_cabin_test <- titanic_full_cat_casted %>%
  filter(is.na(Cabin)) %>%
  select(PassengerId, Pclass, Sex, SibSp, Parch, Fare, Embarked)
length(titanic_cabin_label)
dim(titanic_cabin_train)
dim(titanic_cabin_test)
colSums(is.na(titanic_cabin_train))
colSums(is.na(titanic_cabin_test))
sum(is.na(titanic_cabin_label))
```
# finding missing values in Cabin
```{r}
cabin_result <- knn(train = titanic_cabin_train,
                    test = titanic_cabin_test,
                    cl = titanic_cabin_label, 
                    k = 7)
head(cabin_result)
titanic_full[is.na(titanic_full$Cabin), "Cabin"] <- cabin_result
```
# mutate cabin
```{r}
titanic_full <- titanic_full %>%
  mutate(Cabin = str_sub(string = titanic_full$Cabin,  
                         start = 1, 
                         end = 1))
str(titanic_full)
colSums(is.na(titanic_full))
```
## Age Imputation
# prep
```{r}
colSums(is.na(titanic_full))
bp_Age <- boxplot(titanic_full$Age)
```
# filter
```{r}
boxplot.stats(titanic_full$Age)
age_upper_wishker <- boxplot.stats(titanic_full$Fare)$stats[5] 
age_upper_wishker
```
```{r}
age_outlier_filter <- titanic_full$Age < age_upper_wishker
titanic_filtered_with_age <- titanic_full[age_outlier_filter,]
colSums(is.na(titanic_filtered_with_age))
```
# check filter
```{r}
titanic_filtered_with_age_and_without_NA <- titanic_filtered_with_age %>%
  select(-Survived, -PassengerId, -Name) %>%
  drop_na()

sum(is.na(titanic_filtered_with_age_and_without_NA))
```
# find the missing variables 
```{r}
age_equation = "Age ~ Pclass + Sex + Fare + SibSp + Parch + Embarked + Cabin"
age_model <- lm(formula = age_equation, 
                 data = titanic_filtered_with_age_and_without_NA)
age_model
data_with_missing_age <- titanic_full[is.na(titanic_full$Age), 
                           c("Pclass", "Sex", "Fare", "SibSp", "Parch", "Embarked", "Cabin")]
head(data_with_missing_age)
```
```{r}
lm(formula = age_equation, data = titanic_filtered_with_age_and_without_NA)
```
```{r}
age_prediction <- predict(age_model, newdata = data_with_missing_age)
head(age_prediction, n=20)
```
```{r}
titanic_full[is.na(titanic_full$Age), "Age"] <- age_prediction

colSums(is.na(titanic_full))
```
## Survived?
```{r}
titanic_full %>%
  summarize_all(n_distinct)
titanic_full_cat_casted2 <- titanic_full %>%
  mutate(Pclass = as.factor(Pclass),
         Sex = as.factor(Sex),
         SibSp = as.factor(SibSp),
         Parch = as.factor(Parch),
         Cabin = as.factor(Cabin),
         Embarked = as.factor(Embarked)
  )
str(titanic_full_cat_casted2)
```
#spilt data frames back into test and train
```{r}
titanic_train_2 <- titanic_full_cat_casted2[titanic_full_cat_casted2$is_train_set == TRUE,]
titanic_test_2 <- titanic_full_cat_casted2[titanic_full_cat_casted2$is_train_set == FALSE,]
table(ttr = dim(titanic_train), 
      ttr2 = dim(titanic_train_2))
table(tt = dim(titanic_test),
      tt2 = dim(titanic_test_2))
sum(is.na(titanic_train_2$Survived))
titanic_train_2$Survived <- as.factor(titanic_train_2$Survived)
```
## Prediction 
```{r}
survived_equation = "Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Cabin + Embarked"
survived_formula <- as.formula(survived_equation)

library("ranger")

titanic_ranger_model <- ranger(formula = survived_formula, 
                               data = titanic_train_2,
                               num.trees = 10000,
                               seed = 99,
                               classification = TRUE)

titanic_ranger_model
```
```{r}
titanic_survived <- predict(titanic_ranger_model, data = titanic_test_2)
str(titanic_survived)


PassengerId <- titanic_test_2$PassengerId
titanic_output <- as.data.frame(PassengerId)
titanic_output$Survived <- titanic_survived$predictions
str(titanic_output)

```


