---
title: data classes
author: ''
date: '2022-02-23'
slug: data-classes
categories:
  - data wrangling
  - R
tags:
  - R Markdown
---
## factors 
R uses factors to handle categorical variables, variables that have a fixed and known set of possible values

```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x
typeof(x)
class(x)
```
We can think of factors like character (level labels) and an integer (level numbers) glued together
```{r}
as.integer(x)
```
##dates 
```{r}
y <- as.Date("2020-01-01")
y
typeof(y)
class(y)
```
We can think of dates like an integer (the number of days since the origin, 1 Jan 1970) and an integer (the origin) glued together
```{r}
as.integer(y)
as.integer(y) / 365 # roughly 50 yrs
```
## Data frames 
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df
typeof(df)
class(df)
df
```
## Lists 
```{r}
l <- list(
  x = 1:4,
  y = c("hi", "hello", "jello"),
  z = c(TRUE, FALSE)
)
1
sum(1)
```
## lists and data frames 
A data frame is a special list containing vectors of equal length
When we use the pull() function, we extract a vector from the data frame

## call tidyverse
```{r}
library(tidyverse)
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/cat-lovers.csv'
cat_lovers <- read_csv(url)
glimpse(cat_lovers)
ggplot(cat_lovers, mapping = aes(x = handedness)) +
  geom_bar()
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```
## hotels 
```{r}
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/hotels.csv'
hotels <- read_csv(url)
glimpse(hotels)
```
## lubridate
lubridate is the tidyverse-friendly package that makes dealing with dates a little easier
```{r}
install.packages("tidyverse")
library(lubridate)
```
## dates
slide 22-the end shows how to use them..
  

