---
title: 'A02: Regression Models'
author: R package build
date: '2022-03-24'
slug: a02-regression-models
categories: []
tags: []
---
##Loading and prepaping the data
```{r}
library(pacman)
library(magrittr)
library(psych)
library(RColorBrewer)
library(tidyverse)
library(boot)
library(patchwork)

```

```{r}
professorproposes <- read_csv("https://raw.githubusercontent.com/csanford2020/professor_propose/main/Professor_Proposes_Data.csv")
```

```{r}
names(professorproposes)
```

```{r}
summary(professorproposes)

```

```{r}
df <- professorproposes %>%
  as_tibble() %>%
  print()

```

```{r}
summary(df)
```

## Frequencies of the variables

```{r}

df %>% count(Cut)
cut <- df %>%
  ggplot() +
  geom_bar(aes(Cut, fill = Cut)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )
df %>% count(Clarity)
clarity <- df %>%
  ggplot() +
  geom_bar(aes(Clarity, fill = Clarity)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )
df %>% count(Certification)
certification <- df %>%
  ggplot() +
  geom_bar(aes(Certification, fill = Certification)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )
df %>% count(Polish)
polish <- df %>%
  ggplot() +
  geom_bar(aes(Polish, fill = Polish)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )
df %>% count(Symmetry)
symmetry <- df %>%
  ggplot() +
  geom_bar(aes(Symmetry, fill = Symmetry)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )
cut + clarity + certification + polish + symmetry
```
## Comparing the variables with Price
```{r}
carat <- ggplot(data = df, 
       mapping = aes(x = Carat, y = Price,
                     colour = Wholesaler)) +
  geom_point() 
color <- ggplot (df, aes(x = Colour, y = Price)) +
  geom_boxplot()
cut <- ggplot (df, aes(x = Cut, y = Price)) +
  geom_boxplot()
clarity <- ggplot (df, aes(x = Clarity, y = Price)) +
  geom_boxplot()
certification <- ggplot (df, aes(x = Certification, y = Price)) +
  geom_boxplot()
polish <- ggplot (df, aes(x = Polish, y = Price)) +
  geom_boxplot()
symmetry <- ggplot (df, aes(x = Symmetry, y = Price)) +
  geom_boxplot()
 carat + cut + color + clarity + certification + polish + symmetry 
```

## based off the graphs the carat size of the diamond and the color primariliy impacts the prize of  the diamond

## variables that effect the Carat
```{r}
cut <- ggplot (df, aes(x = Cut, y = Carat)) +
  geom_boxplot()
color <- ggplot (df, aes(x = Colour, y = Carat)) +
  geom_boxplot()
clarity <- ggplot (df, aes(x = Clarity, y = Carat)) +
  geom_boxplot()
certification <- ggplot (df, aes(x = Certification, y = Carat)) +
  geom_boxplot()
polish <- ggplot (df, aes(x = Polish, y = Carat)) +
  geom_boxplot()
symmetry <- ggplot (df, aes(x = Symmetry, y = Carat)) +
  geom_boxplot()
cut +  color + clarity + certification + polish + symmetry 
```
# no variables have an effect of carat
## Variables that effect Color of diamond
```{r}
cut <- ggplot (df, aes(x = Carat, y = Colour)) +
  geom_boxplot()
color <- ggplot (df, aes(x = Cut, y = Colour)) +
  geom_boxplot()
clarity <- ggplot (df, aes(x = Clarity, y = Colour)) +
  geom_boxplot()
certification <- ggplot (df, aes(x = Certification, y = Colour)) +
  geom_boxplot()
polish <- ggplot (df, aes(x = Polish, y = Colour)) +
  geom_boxplot()
symmetry <- ggplot (df, aes(x = Symmetry, y = Colour)) +
  geom_boxplot()
carat+ color + clarity + certification + polish + symmetry 

```
# cut and carat seems to effect the color of the diamond so I will use the carat in the linear model

## linear regression
```{r}
lmPrice <- lm(Carat ~ Price, data = professorproposes)
coef(lmPrice)
lmPrice <- lm(Carat ~ Price, data = professorproposes)
lmPrice
```


## Linear regression for all the variables

```{r}
linearMod <- lm(Carat ~ Symmetry, data=df)
print(linearMod)
```


## bootstrap

```{r}
set.seed(1)
head(df)
dim(df)
train <- sample(450, 200)
head(train)
```

```{r}
boot.fn <- function(df, index){
  return(coef(lm(`Carat`~`Price`, data = df, subset = index)))
}

```

```{r}
boot.fn(df, 1:450)
```
```{r}
set.seed(1)
boot.fn(df, sample(450, 450, replace = T))
```






