---
title: Data IO
author: ''
date: '2022-02-23'
slug: data-io
categories: []
tags: []
---
## reader 
read_csv() - comma delimited files
read_csv2() - semicolon separated files (common in countries where , is used as the decimal place)
read_tsv() - tab delimited files
read_delim() - reads in files with any delimiter
read_fwf() - fixed width files
...
## readxl
read_excel() - read xls or xlsx files
## reading data
```{r}
library(tidyverse)
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/nobel.csv'
nobel <- read_csv(url)
nobel
```
## writing data
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "example")
read_csv("example")
```
## my turn
```{r}
library(tidyverse)
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/nobel.csv'
nobel <- read_csv(url)
nobel




```

## bad names
```{r}
library(tidyverse)
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/edibnb-badnames.csv'
edibnb_badnames <- read_csv(url)
edibnb_badnames
```
## colum types 
type function	data type
col_character()	character
col_date()	date
col_datetime()	POSIXct (date-time)
col_double()	double (numeric)
col_factor()	factor
col_guess()	let readr guess (default)
col_integer()	integer
col_logical()	logical
col_number()	numbers mixed with non-number characters
col_numeric()	double or integer
col_skip()	do not read
col_time()	time

## fav food 
```{r}
library(tidyverse)
url <- 'https://raw.githubusercontent.com/csanford2020/tidyverse/main/fav-food-clean.csv'
fav_food <- read_csv(url)
fav_food
```
## other types of data 
googlesheets4: Google Sheets
haven: SPSS, Stata, and SAS files
DBI, along with a database specific backend (e.g. RMySQL, RSQLite, RPostgreSQL etc): allows you to run SQL queries against a database and return a data frame
jsonline: JSON
xml2: xml
rvest: web scraping
httr: web APIs
sparklyr: data loaded into spark



