---
title: 'Palmer Penguins visulization '
author: ''
date: '2022-02-09'
slug: palmer-penguins-visulization
categories:
  - R
tags:
  - penguins
  - GGPLOT2
---
## Palmer Penguins
```{r}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```


```{r warning=FALSE}
```


```{r warning=FALSE}
```


```{r warning=FALSE}
```
> library(tidyverse)
-- Attaching packages ---------------- tidyverse 1.3.1 --
v ggplot2 3.3.5     v purrr   0.3.4
v tibble  3.1.6     v dplyr   1.0.7
v tidyr   1.2.0     v stringr 1.4.0
v readr   2.1.2     v forcats 0.5.1
-- Conflicts ------------------- tidyverse_conflicts() --
x dplyr::filter() masks stats::filter()
x dplyr::lag()    masks stats::lag()
> 
> library(tidyverse)
> 
> library(palmerpenguins)
Error in library(palmerpenguins) : 
  there is no package called ‘palmerpenguins’
> library(tidyverse)
> library(palmerpenguins)
Error in library(palmerpenguins) : 
  there is no package called ‘palmerpenguins’
> glimpse(penguins)
Error in glimpse(penguins) : object 'penguins' not found
> install.packages("palmerpenguins")
WARNING: Rtools is required to build R packages but is not currently installed. Please download and install the appropriate version of Rtools before proceeding:

https://cran.rstudio.com/bin/windows/Rtools/
Installing package into ‘C:/Users/cmsan/OneDrive/Documents/R/win-library/4.1’
(as ‘lib’ is unspecified)
trying URL 'https://cran.rstudio.com/bin/windows/contrib/4.1/palmerpenguins_0.1.0.zip'
Content type 'application/zip' length 3003085 bytes (2.9 MB)
downloaded 2.9 MB

package ‘palmerpenguins’ successfully unpacked and MD5 sums checked

The downloaded binary packages are in
	C:\Users\cmsan\AppData\Local\Temp\RtmpCoH3n2\downloaded_packages
> 
> library(tidyverse)
> library(palmerpenguins)
> glimpse(penguins)
Rows: 344
Columns: 8
$ species           <fct> Adelie, Adelie, Adelie, ~
$ island            <fct> Torgersen, Torgersen, To~
$ bill_length_mm    <dbl> 39.1, 39.5, 40.3, NA, 36~
$ bill_depth_mm     <dbl> 18.7, 17.4, 18.0, NA, 19~
$ flipper_length_mm <int> 181, 186, 195, NA, 193, ~
$ body_mass_g       <int> 3750, 3800, 3250, NA, 34~
$ sex               <fct> male, female, female, NA~
$ year              <int> 2007, 2007, 2007, 2007, ~
> 
> 
> ## Scatter plot
> ggplot(data = penguins, 
+        mapping = aes(x = bill_depth_mm, y = bill_length_mm,
+                      colour = species)) +
+     geom_point() +
+     labs(title = "Bill depth and length",
+          subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
+          x = "Bill depth (mm)", y = "Bill length (mm)",
+          colour = "Species")
Warning message:
Removed 2 rows containing missing values (geom_point). 
> library(tidyverse)
> library(palmerpenguins)
> glimpse(penguins)
Rows: 344
Columns: 8
$ species           <fct> Adelie, Adelie, Adelie, ~
$ island            <fct> Torgersen, Torgersen, To~
$ bill_length_mm    <dbl> 39.1, 39.5, 40.3, NA, 36~
$ bill_depth_mm     <dbl> 18.7, 17.4, 18.0, NA, 19~
$ flipper_length_mm <int> 181, 186, 195, NA, 193, ~
$ body_mass_g       <int> 3750, 3800, 3250, NA, 34~
$ sex               <fct> male, female, female, NA~
$ year              <int> 2007, 2007, 2007, 2007, ~
> ggplot(data = penguins, 
+        mapping = aes(x = bill_depth_mm, y = bill_length_mm,
+                      colour = species)) +
+     geom_point() +
+     labs(title = "Bill depth and length",
+          subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
+          x = "Bill depth (mm)", y = "Bill length (mm)",
+          colour = "Species")
Warning message:
Removed 2 rows containing missing values (geom_point). 
> ggplot(data = penguins,
+        mapping = aes(x = bill_depth_mm,
+                      y = bill_length_mm,
+                      colour = species)) +
+     geom_point() +
+     labs(title = "Bill depth and length",
+          subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
+          x = "Bill depth (mm)", y = "Bill length (mm)",
+          colour = "Species",
+          caption = "Source: Palmer Station LTER / palmerpenguins package") +
+     scale_colour_viridis_d()
Warning message:
Removed 2 rows containing missing values (geom_point). 
> Start with the penguins data frame, map bill depth to the x-axis and map bill length to the y-axis. Represent each observation with a point and map species to the colour of each point. Title the plot "Bill depth and length", add the subtitle "Dimensions for Adelie, Chinstrap, and Gentoo Penguins", label the x and y axes as "Bill depth (mm)" and "Bill length (mm)", respectively, label the legend "Species", and add a caption for the data source. Finally, use a discrete colour scale that is designed to be perceived by viewers with common forms of colour blindness.
Error: unexpected symbol in "Start with"
> ## Aesthetics 
> ggplot(penguins,
+        aes(x = bill_depth_mm, 
+            y = bill_length_mm,
+            colour = species,
+            shape = species,
+            size = body_mass_g,
+            alpha = flipper_length_mm)) +
+     geom_point() +
+     scale_colour_viridis_d()
Warning message:
Removed 2 rows containing missing values (geom_point). 
> ## Faceting 
> ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + 
+     geom_point() +
+     facet_grid(species ~ island)
Warning message:
Removed 2 rows containing missing values (geom_point). 
> ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + 
+     geom_point() +
+     facet_grid(species ~ sex)
Warning message:
Removed 2 rows containing missing values (geom_point). 
> ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + 
+     geom_point() +
+     facet_wrap(~ species)
Warning message:
Removed 2 rows containing missing values (geom_point). 
> ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + 
+     geom_point() +
+     facet_wrap(~ species, ncol = 2)
Warning message:
Removed 2 rows containing missing values (geom_point). 
