---
title: 'Professor Evaluations '
author: ''
date: '2022-02-28'
slug: professor-evaluations
categories: []
tags: []
---
## preliminaries 
``` {r}
library(moderndive)
library(tidyverse)
library(skimr)
library(gapminder)

```
##  Exploratory data analysis
``` {r}
evals_ch5 <- evals %>%
  select(ID, score, bty_avg, age)
glimpse(evals_ch5)
evals_ch5 %>%
  sample_n(size = 5)
```
## exploring the data
``` {r}
glimpse(evals_ch5)

```
## Sample the data 
``` {r}
evals_ch5 %>%
  sample_n(size = 5)
```
## Mean and Median of BTY and Score 
``` {r}
evals_ch5 %>%
  summarize(mean_bty_avg = mean(bty_avg), mean_score = mean(score),
            median_bty_avg = median(bty_avg), median_score = median(score))

```

## five number summary 
```{r}
evals_ch5 %>% select(score, bty_avg) %>% skim()

```
## visualizing data 
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(x = "Beauty Score", 
       y = "Teaching Score",
       title = "Scatterplot of relationship of teaching and beauty scores")

```

## adding jitter 
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_jitter() +
  labs(x = "Beauty Score", y = "Teaching Score",
       title = "Scatterplot of relationship of teaching and beauty scores")
```

## relationship between beauty and teaching scores 
```{r}
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
  geom_point() +
  labs(x = "Beauty Score", y = "Teaching Score",
       title = "Relationship between teaching and beauty scores") +  
  geom_smooth(method = "lm", se = FALSE)
```
## simple linear regression
```{r}
# Fit regression model:
score_model <- lm(score ~ bty_avg, data = evals_ch5)
# Get regression table:
get_regression_table(score_model)

# Fit regression model:
score_model <- lm(score ~ bty_avg, data = evals_ch5)
# Get regression table:
get_regression_table(score_model)

```
##Observed/fitted values and residuals
```{r}
regression_points <- get_regression_points(score_model)
regression_points

```
The score column represents the observed outcome variable  
y
 . This is the y-position of the 463 black points.
The bty_avg column represents the values of the explanatory variable  
x
 . This is the x-position of the 463 black points.
The score_hat column represents the fitted values  
ˆ
y
 . This is the corresponding value on the regression line for the 463  
x
  values.
The residual column represents the residuals  
y
−
ˆ
y
 . This is the 463 vertical distances between the 463 black points and the regression line.
##One categorical explanatory variable
It’s an unfortunate truth that life expectancy is not the same across all countries in the world. International development agencies are interested in studying these differences in life expectancy in the hopes of identifying where governments should allocate resources to address this problem. In this section, we’ll explore differences in life expectancy in two ways:

Differences between continents: Are there significant differences in average life expectancy between the five populated continents of the world: Africa, the Americas, Asia, Europe, and Oceania?
Differences within continents: How does life expectancy vary within the world’s five continents? For example, is the spread of life expectancy among the countries of Africa larger than the spread of life expectancy among the countries of Asia?
To answer such questions, we’ll use the gapminder data frame included in the gapminder package. This dataset has international development statistics such as life expectancy, GDP per capita, and population for 142 countries for 5-year intervals between 1952 and 2007. Recall we visualized some of this data in Figure 2.1 in Subsection 2.1.2 on the grammar of graphics.

We’ll use this data for basic regression again, but now using an explanatory variable  
x
  that is categorical, as opposed to the numerical explanatory variable model we used in the previous Section 5.1.

A numerical outcome variable  
y
  (a country’s life expectancy) and
A single categorical explanatory variable  
x
  (the continent that the country is a part of).
When the explanatory variable  
x
  is categorical, the concept of a “best-fitting” regression line is a little different than the one we saw previously in Section 5.1 where the explanatory variable  
x
  was numerical. We’ll study these differences shortly in Subsection 5.2.2, but first we conduct an exploratory data analysis.
##Exploratory data analysis
```{r}
library(gapminder)
gapminder2007 <- gapminder %>%
  filter(year == 2007) %>%
  select(country, lifeExp, continent, gdpPercap)
glimpse(gapminder2007)

```
## Random Sample of the data
```{r}
gapminder2007 %>% sample_n(size = 5)

```
### summarizing whole data
```{r}
gapminder2007 %>%
  select(lifeExp, continent) %>%
  skim()
```
## GGplot of life expactancies 
```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies")
```
##Adding Facet 
```{r}
ggplot(gapminder2007, aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(x = "Life expectancy", 
       y = "Number of countries",
       title = "Histogram of distribution of worldwide life expectancies") +
  facet_wrap(~ continent, nrow = 2)
```
## Alternative way of graphing life expectancies 
```{r}
ggplot(gapminder2007, aes(x = continent, y = lifeExp)) +
  geom_boxplot() +
  labs(x = "Continent", y = "Life expectancy",
       title = "Life expectancy by continent")
```
##Computing the mean and median of life expectancy
```{r}
lifeExp_by_continent <- gapminder2007 %>%
  group_by(continent) %>%
  summarize(median = median(lifeExp), 
            mean = mean(lifeExp))

```
##  Linear regression of life expectancy 
```{r}
lifeExp_model <- lm(lifeExp ~ continent, data = gapminder2007)
get_regression_table(lifeExp_model)

```
## Observed/fitted values and residuals for life expectanies
```{r}
regression_points <- get_regression_points(lifeExp_model, ID = "country")
regression_points
```
## Chapter website used 
https://moderndive.netlify.app/5-regression.html#model2
